Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-18 chi2012.tex
Moved titles of survey results and resized:wq
Shrunk multipathing image
Table made for PS2

%% TODO THIS IS PLACEHOLDER DATA >> 
\begin{table*}
\small
\begin{tabular}{| p{2.0cm} | p{1.5cm} | p{3.6cm} | p{2cm} | p{2cm} | l | l | l | l |}
\hline
source category  & data type & sources & API type & avg fields/rec & avg depth & term. & struct & semantic \\
\hline
social networking  & person's profile & Facebook, LinkedIn, Google+ & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 & 1.0 \\
event calendars & events & Eventbrite, Google Calendar  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 & 1.0 \\
retail (shopping)  & product profile & Amazon, Shopping.com, Etsy, Groupon, Zappos  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 & 1.0 \\
music catalogues & songs and albums & Echonest, rdio, Soundcloud, Spotify  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 & 1.0 \\
weather & forecasts & W.Underground, Weatherbug, Yahoo! Weather & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 & 1.0 \\
\hline
\end{tabular}
\caption{\emph{PS.2 Results} - Analysis of heterogeneity present across data feeds, by category of feed}\label{tbl:prestudy2}
\end{table*}
%% <<

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{img/multipathing}
\caption{To see properties, users click on the name of the property. When instances do not have a particular property, additional property names can be added.}
\label{fig:multipathing}
\end{center}
\end{figure}

@@

\begin{figure}[tbp]
\begin{center}
\includegraphics[width=8.5cm]{img/survey}
\caption{\emph{Survey results} - Answers to questions on a 5-point Likert scale, from 1-\emph{strongly disagree} to 5-\emph{strongly agree}.}
\label{fig:survey}
\end{center}
\end{figure}

>>>>

\begin{table*}
\small
\begin{tabular}{| p{2.0cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} | p{1.8cm} |}
\hline
				& {\bf source}		& {\bf average props/record}	& {\bf average depth/record}	& {\bf equivalent to}	& {\bf prop name inconsistent}	& {\bf structural inconsistency} 	& {\bf model inconsistency} \\
\hline
social networking	& google+			& 12						& 1.52					& tw:5, li:4, fb:4		& tw:3, li:2, fb:2				& tw:0, li:1, fb:1				& tw:0, li:0, fb:0 \\
(profiles)			& twitter			& 39						& 1.37					& li:4, fb:4 			& li:2, fb:1					& li:0, fb:0					& li:0, fb:0 \\
				& linkedin			& 18						& 2.42					& fb:7			& fb:5					& fb:3					& fb:0 \\
				& facebook		& 22						& 1.5						&				&						&						& \\
\hline
calendars			& google calendar	& 15						& 1.46					& eb:9			& eb:6					& eb:1					& eb:1 \\
(events)			& eventbrite		& 32						& 1.43					&				&						& 						& \\
\hline
retail				& milo			& 5						& 1.2						& z:2, s:3, e:1, a:3	& z:2, s:2, e:1, a:3			& z:0, s:0, e:0, a:2			& z:0, s:0, e:0, a:0 \\
(products)			& zappos			& 6						& 1						& s:2, e:2, a:3		& s:2, e:2, a:2				& s:0, e:0, a:0				& s:0, e:0, a:0 \\
				& shopping.com	& 11						& 3.74					& e:2, a:8			& e:2, a:8					& e:0, a:0					& e:0, a:0 \\
				& etsy			& 31						& 1.13					& a:11			& a:10					& a:1						& a:2 \\
				& amazon			& 108					&						&				& 						&						& \\
\hline
contacts			& google contacts	& 7						& 1.46					& yp:2			& yp:2					& yp: 0					& yp: 0 \\
				& yellowpages		& 25						& 1						&				&						&						& \\
\hline
music			& echonest		& 4						& 1.83					& so:3, r:3, sp:3		& so:3, r:3, sp:3				& so:0, r:0, sp:0				& so:0, r:0, sp:0 \\
(songs/			& soundcloud		& 42						& 2.14					& r:12, sp:7		& r:11, sp:6 				& r:1, sp:1					& r:1, sp:0 \\
tracks)			& rdio			& 27						& 2						& sp: 7			& sp: 6					& sp: 1					& sp: 1 \\
				& spotify			& 10						& 2.44					&				&						&						& \\
\hline
weather			& weatherbug		& 8						& 2						& wu: 5, y: 5		& wu: 5, y: 5				& wu: 5, y: 4				& wu: 0, y: 0 \\
(forecasts)		& wundergound	& 52						& 1.38					& y:12			& y:12					& y:7						& y:3 \\
				& yahoo weather	& 22						& 1.58					&				&						&						& \\
\hline
\end{tabular}
\caption{\emph{PS.2 Results} - Analysis of heterogeneity present across data feeds, by category of feed}\label{tbl:prestudy2}
\end{table*}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8.5cm]{img/multipathing}
\caption{To see properties, users click on the name of the property. When instances do not have a particular property, additional property names can be added.}
\label{fig:multipathing}
\end{center}
\end{figure}

@@

\begin{figure}[tbp]
\begin{center}
\includegraphics[width=7.5cm]{img/survey}
\caption{\emph{Survey results} - Answers to questions on a 5-point Likert scale, from 1-\emph{strongly disagree} to 5-\emph{strongly agree}.}
\label{fig:survey}
\end{center}
\end{figure}
